Summary Tables

### 2020-02-12 summary_tables_outcomes.Rmd
Add cross references

Click here: [change in yll](#change_yll_100k)

>>>>

```
* [change in yll](#change_yll_100k)
* [Change in total deaths](#change_death)
* [Change in deaths per 100k](#change_death_100k)
* [Change in total YLLs](#change_YLL)
* [Change in YLLs by age per 100k](#change_YLL_age_100k)
* [Change in YLLs by gender by age per 100k](#change_in_YLL_gender_age_100k)
* [Change in deaths due to injury](#change_death_injury)
* [Change in deaths due to PA](#change_death_PA)
* [Change in deaths due to AP](#change_death_AP)
* [Change in deathe due to injury per 100k](#change_death_injury_100k)
* [Change in deahts due to PA per 100k](#change_death_PA_100k)
* [Change in deaths due to AP per 100k](#change_death_AP_100k)
* [Change in YLLs due to injury](#change_yll_injury)
* [Change in YLLs due to PA](#change_yll_PA)
* [Change in YLLs due to Ap](#change_yll_AP)
* [Change in YLLs due to injury per 100k](#change_yll_injury_100k)
* [Change in YLLs due to PA per 100k](#change_yll_PA_100k)
* [Change in YLLs due to AP per 100k](#change_yll_AP_100k)
* [Change in deaths by disease due per 100k](#change_death_disease_100k)
* [Change in YLLs by disease](#change_yll_disease)
* [Change in deaths due per 100k](#change_yll_disease_100k)
